Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-12-19 manuscript.tex
updated manuscript

Let's examine an example. Assume three response options (wrong, neither,
right). Assume further that each of the three responses was selected by
a third of participants, i.e., the distributions of responses is 1/3,
1/3, and 1/3. Under the Strong link, we infer that this task yielded an
implicature rate of 2/3. Under the Weak link, we infer that this task
yielded an implicature rate of 1/3. This is quite a drastic difference
if we are, for instance, interested in whether scalar implicatures are
inference defaults and we would like to interpret an implicature rate of
above an arbitrary threshold (e.g., 50\%) as evidence for such a claim.
Under the Strong link, we would conclude that scalar implicatures are
not defaults. Under the Weak link, we would conclude that they are. In
the experiment reported in the following section, we presented
participants with exactly this setup. We manipulated the number of
response options between participants and analyzed the results under
different linking hypothesis.

>>>>

Let's examine an example. Assume three response options (wrong, neither,
right). Assume further that each of the three responses was selected by
a third of participants, i.e., the distributions of responses is 1/3,
1/3, and 1/3. Under the Strong link, we infer that this task yielded an
implicature rate of 2/3. Under the Weak link, we infer that this task
yielded an implicature rate of 1/3. This is quite a drastic difference
if we are, for instance, interested in whether scalar implicatures are
inference defaults and we would like to interpret an implicature rate of
above an arbitrary threshold (e.g., 50\%) as evidence for such a claim.
Under the Strong link, we would conclude that scalar implicatures are
not defaults. Under the Weak link, we would conclude that they are. In
the experiment reported in the following section, we presented
participants with exactly this setup. We manipulated the number of
response options between participants and analyzed the results under
different linking hypothesis.\footnote{\change{Researchers may vary with respect to which linking hypothesis (Weak vs.~Strong, or others) they consider most plausible. Supporters of the Weak link may argue that there are three theoretically motivated categories of judgments: false, true but infelicitous, true and felicitous. Under such an account, it is plausible that false and true+felicitous responses occupy the ends of the false/true scale while true but infelicitous responses occupy the mid portion. On critical trials, participants judge underinformative statements that are true but infelicitous and therefore the mid portion of the scale can provide evidence for implicature computation. However, supporters of the Strong link may argue that if a participant computes an implicature, their response in the task should show the commitment to that interpretation by judging the underinformative utterance as false. Any other response shows that they have not truly computed an implicature. So far, these discussions have remained largely informal. In this paper we stay neutral with respect to the plausibility of each link and only aim to demonstrate the consequences of assuming them.}}
